SPA: An Apache Spark Pilot scheduler\\ for HPC applications

### 2019-04-29 paper.tex
modified abstract

\begin{abstract}
    Big Data processing engines such as Apache Spark are increasingly 
    used to process scientific data. These processing engines, however, 
    have been primarily designed to work on dedicated infrastructure 
    and are not well designed to work on High-Performance Computing 
    (HPC) systems commonly available to researchers. Typical mechanisms 
    for launching Spark-based applications on HPC clusters involve 
    batch-requesting of the resources which can greatly increase 
    queuing times of the Big Data applications. Pilot scheduling is a 
    well known strategy that decouples resource provisioning from task 
    scheduling, thereby allowing applications to leverage dynamic 
    pools of computing resources. Here, we introduce SPA, an 
    open-source
    pilot-job submission system designed for launching Apache Spark pipelines 
    on Slurm-based clusters. SPA leverages optimizations available in Spark, 
    such as robust workers, masters and driver, in addition to 
    checkpointing, to ensure robustness against nodes lost due to
    expired walltime. SPA also ensures that a 
    user-specified number of pilots is maintained in the cluster in 
    order to ensure a constant level of parallelism. Should pilots be 
    idle for a certain amount of time, they are terminated by 
    the system. We evaluate SPA on neuroimaging pipelines, our main domain of interest. \tristan{Add a sentence on results when you have them.}

\end{abstract}

@@

\section{Materials and Methods}\label{sec:methods}
    \todo{walltime parameter of workflow}
    \subsection{Added value of pilot scheduling}
        \todo{execution of a batch cluster vs dynamic (pilot) cluster}
    \subsection{Robust masters}
        \todo{scala standalone vs our pyspark workaround. kill masters in experiments}
    \subsection{Checkpointing}
        \todo{metric for determining how often to checkpoint based on cluster size}
    \subsection{Job arrays}
        \todo{need to kill idle workers. may not want all workers to be running at once.}
    \subsection{Example application}
        \todo{incrementation with varying task durations}
\section{Discussion}\label{sec:discussion}
\section{Conclusion}\label{sec:conclusion}

>>>>

\begin{abstract}
    Big Data has become prominent throughout many scientific fields and, as a
    result, scientific communities have sought out Big Data frameworks to 
    accelerate the processing of their increasingly data-intensive pipelines.
    However, while scientific communities typically rely on High-Performance 
    Computing (HPC) clusters for the parallelization of their pipelines, many 
    popular Big Data frameworks such as Hadoop and Spark were primarily designed
    to be executed on dedicated commodity infrastructure. Differences found between
    these infrastructures and the policies that surround them limit the advantages
    of deploying Big Data pipelines on HPC infrastructure. For instance, HPC
    clusters typically employ a batch job submission system requiring users to
    specify details on number of cores, nodes, amount of memory and duration.
    Big Data engines, such as Spark, have no built-in mechanism to interact with
    HPC batch job submission systems. Morever, the details required by the HPC
    schedulers are not necessarily initially known to users of Big Data frameworks.

    Pilot scheduling strategies have been developed to address the limitations 
    of traditional HPC batch job schedulers. Pilot schedulers decouple resource
    provisioning from task scheduling, thereby enabling efficient resource
    utilization through dynamic scheduling. This paper evaluates the benefits 
    pilot-scheduling strategies over traditional batch submission
    on HPC clusters with overlay Apache Spark clusters. We first evaluate the
    overall speedup brought on by employing pilot-scheduling strategies. We then
    examine the robustness to master and driver failures, which may be frequent 
    when underestimating pilot walltime. Spark built-in checkpointing is also 
    investigated in relation to pilot expiration.

    Our results show that\ldots TBD.
\end{abstract}

@@

\section{Materials and Methods}\label{sec:methods}
    SPA consists of a Python-based driver with bash-templates that are called 
    using the Slurmpy~\cite{slurmpy} library. In order to commence pilot-scheduling,
    the user must supply the bash template of choice and a JSON configuration 
    file which contains details on pilot node requirements and the desired application
    to be launched. Currently, there only exists a single pilot template for launching
    Spark jobs on a Slurm-based HPC cluster. The pseudocode for that template can 
    be seen in ~\ref{Figure:pilot-temp}.
    \todo{walltime parameter of workflow}
    \subsection{Added value of pilot scheduling}
        \todo{execution of a batch cluster vs dynamic (pilot) cluster}
    \subsection{Robust masters}
        \todo{scala standalone vs our pyspark workaround. kill masters in experiments}
    \subsection{Checkpointing}
        \todo{metric for determining how often to checkpoint based on cluster size}
    \subsection{Job arrays}
        \todo{need to kill idle workers. may not want all workers to be running at once.}
    \subsection{Example application}
        \todo{incrementation with varying task durations}
\section{Discussion}\label{sec:discussion}
\section{Conclusion}\label{sec:conclusion}
